---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "140%"
)
```
# sifr: search in files 

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://lifecycle.r-lib.org/articles/stages.html)
<!-- badges: end -->

sifr is a tool for searching text strings and regular expression patterns 
recursively in directory trees from within R. It supports colored console 
output, RStudio source markers, and can also return the search results as
a `data.frame` for further processing. In addition, sifr provides 
`sed_replace()` on supported platforms (such as Linux, BSD, macOS) for replacing 
regex patterns across directory trees via [sed](https://en.wikipedia.org/wiki/Sed).


## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("s-fleck/sifr")
```
## Example

```{r example}
library(sifr)

tf <- tempfile(fileext = ".csv")
write.csv(cars, tf)

x <- sif("26", dir = dirname(tf), markers = FALSE, path_pattern = ".*\\.csv$")
print(x)
as.data.frame(x)


sed_replace("26", "twentysix", dir = dirname(tf), path_pattern = ".*\\.csv$")
sif("26", dir = dirname(tf), markers = FALSE, path_pattern = ".*\\.csv$")
sif("twentysix", dir = dirname(tf), markers = FALSE, path_pattern = ".*\\.csv$")
unlink(tf)
```
